---
title: "Modeling functions"
author: "PyMap"
date: "2023-05-22"
output: html_document
---

```{r, echo=FALSE, meassage=FALSE, warning=FALSE}
library(tidyverse)
library(terra)
library(sf)
library(tmap)
```

# REAL ESTATE MARKET BEHAVIOR MODELING

## 1. LOOK FOR THE PREDOMINANT OFFER TYPE

### Use case: `High & Low Density Building types`

### STEP 1: Load the data and create the target class

```{r, echo=FALSE, message=FALSE}
source("R/datasources.R")
source("R/utils.R")

# Aggregations
# alt 1. Using rename_cat_agg
ppp_recat <- ppp_data_local %>%
rename_cat_agg(cat_col = property_type,
new_col_str = "agg_col",
cat_a = "high-density-types",
cat_b = "low-density-types")
prop.table(table(ppp_recat$agg_col))

# alt 2. Mapping user defined function (non-performing)
#density_types <- map_chr(ppp_data_local$property_type,
#index_cat_agg,
#cat_a_idx = 3, # 3rd yaml key (high)
#cat_b_idx = 4  # 4th yaml key (low density)
#)
#ppp_data_local$density_types <- density_types
#prop.table(table(ppp_data_local$density_types))

source("R/properaty_data.R")
# Load the data (use ppp_recat or ppp_data)
btypes = read_config(path = "config/building_types_agg.yaml")
ppp_sel <- select_building_types(
  input_data = ppp_recat,
  currency = "USD",
  colname = property_type, 
  btypes = c(btypes$`residential-types`), 
  operation = c("Venta"))
```

### STEP 2: Define the analysis zone

#### 2.1. Using Polygons shape file (e.g. target neighborhoods)

```{r, echo=FALSE, warning=FALSE, out.width=900, out.height=350}
# Aggregated offer types
ppp_caba <- ppp_sel %>%
st_as_sf(coords = c("lon", "lat"), crs = 4326)

offer_area <- build_shp_zone(comunes = c(4, 8), ppp_geo = ppp_caba)

tmap_mode("view") +
tm_shape(offer_area) +
tm_dots(col = "tipo_agr",
palette = "RdYlBu",
stretch.palette = TRUE,
size = 0.05,
style = "cont")

```

#### 2.3. Using single polygon geom limits (e.g. drawn area)

```{r, echo=FALSE, warning= FALSE, out.width=900, out.height=350}
offer_area_ <- build_json_zone(str_geom = json_char, ppp_geo = ppp_caba)

tmap_mode("view") +
tm_shape(offer_area_) +
tm_dots(col = "tipo_agr", palette = "RdYlBu",
stretch.palette = TRUE,
size = 0.05, shape = 21,
style = "cont")
```

### STEP 3: Find predominant offer type

#### 3.1. Using the shp polygon limits
```{r}
source("R/models.R")
real_estate_offer(offer_area = offer_area, prediction_method = "orthogonal", intervals = 10, colorsvec = c("lightblue","yellow","purple"))
```
#### 3.2. Using the users drawn polygons
```{r}
real_estate_offer(offer_area = offer_area_, prediction_method = "splines", intervals = 6, colorsvec = c("lightblue","yellow","black"))
```

